---
title: "AD Project Movies: Midpoint Deliverable"
author: "Jeffrey Zhao, Jody Wong, Lynette Li, Zhi Ye"
date: "5/22/2019"
output: html_document
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load results from the analysis
# errors and messages will not be printed given the `include = FALSE` option
source("scripts/chart_one.R")
source("scripts/chart_two.R")
<<<<<<< HEAD
source("scripts/chart_three.R")
#source("scripts/summary_info.R")
=======
source("scripts/summary_info.R")
>>>>>>> 11189871fb03d4db87beaee6a148831800f0caf3
#source("scripts/summary_table.R")

# Load additional libraries that may be needed for output
library("stringr")
library("plotly")
library("knitr")
library("dplyr")
```

```{r, include = FALSE, echo = FALSE}
meta_movie <- read.csv("data/movies_metadata.csv", stringsAsFactors = FALSE)
movies <- read.csv("data/movies.csv", stringsAsFactors = FALSE)
```


# Introduction 
Our synergy in our introductory group discussions brought us to a shared
interest in movies and their back-end processes and facts. Thus, we decided
to explore datasets regarding Movies. Jody enjoys comedies. Lynette and
Jeffrey revel in action movies, especially MCU's Avengers. All in the while,
Zhi appreciates romance. There is more than beneath the eye of paying for a
movie stub at the theater as there are many components before and after movie
releases. Some pre-release factors consisting of budgeting, timeline, and
production planning enhance the quality and enjoyability of the movie. While,
a few post-factors incorporate ratings, price, marketing, and theater
distribution network - all of which aim to drive long-term profitability and
to attract a global audience. We are motivated to analyze movie trends,
statistics, and logistics such as calculating maximum and minimum revenues,
obtaining names of most and least profitable movies or genres, computing the
number of tickets sold per movie, and grouping movies based on
ranges of budgets. The source of the dataset for our project can be found
[here](https://www.kaggle.com/rounakbanik/the-movies-dataset/version/7).

# Summary Paragraph
Within the movies_metadata file, there were significant information
that were interesting. The longest runtime of a movie was
**`r get_summary_info(meta_movie)[1]`** minutes. That movie was
_`r get_summary_info(meta_movie)[2]`_. The movie
_`r get_summary_info(meta_movie)[3]`_, is significant because it has the
highest vote count compared to any other movie. The tagline of
_`r get_summary_info(meta_movie)[3]`_ is
"`r get_summary_info(meta_movie)[4]`" Also, the movie with the highest
revenue is _`r get_summary_info(meta_movie)[5]`_.

# Summary Table 

# Chart 1: Top 10 Most Voted Movies

The purpose of this lollipop chart is to display the top 10 most voted movies.
Each movie is ordered from least to most(left to right). The thin line and 
circle top provides more emphasis on the values of each movie, while giving
it a nice and modern look. 

```{r, echo = FALSE, warning = FALSE}
top_ten_chart <- top_10(meta_movie)
ggplotly(top_ten_chart)
```

- The number one most voted movie is Inception with 14,075 votes.
- The tenth most voted movie from this chart is The Hunger Games, which
has 9,634 votes. 

# Chart 2: Highest Budget on Movie Production Per Year

This chart intends to show the relationship between the maximum budget
amounts for movie production from each year. Budget amounts have increased
over time as a result of many factors, one being currency inflation and
technology equipments and enhancements like CGI used in films.

```{r, echo = FALSE, warning = FALSE}
budget_chart <- budget_by_year(meta_movie)

##Plot Interactive Bar Chart
ggplotly(budget_chart, tooltip = c("year", "max_budget"))
```

<<<<<<< HEAD
- The largest budget spend has been in the year of 2011 with a budget amount of $380 million!
- An upward exponential growth of budgeting is seen to accelerate beginning around the 1970s.
=======
- The largest budget spend has been in the year of 2011 with a budget
amount of 380 million dollars!
- An upward exponential growth of budgeting is seen to accelerate beginning
around the 1970s to 1980s.
>>>>>>> 11189871fb03d4db87beaee6a148831800f0caf3

# Chart 3 (Lynette)
Add Lynette Intro
```{r, echo = FALSE, warning = FALSE}
genre_popular_chart <- popular_genre(movies)

##Plot Interactive Bar Chart
ggplotly(genre_popular_chart)
```

- One observation for lynette
- Two observation for lynette

# Chart 4 (Jeff)
Add Jeff Intro

- One observation for Jeff
- Two observation for Jeff
