---
title: "AD Project Movies: Midpoint Deliverable"
author: "Jeffrey Zhao, Jody Wong, Lynette Li, Zhi Ye"
date: "5/22/2019"
output: html_document
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load results from the analysis
# errors and messages will not be printed given the `include = FALSE` option
source("scripts/chart_one.R")
source("scripts/chart_two.R")
#source("scripts/summary_info.R")
#source("scripts/summary_table.R")

# Load additional libraries that may be needed for output
library("stringr")
library("plotly")
library("knitr")
```

```{r, include = FALSE, echo = FALSE}
meta_movie <- read.csv("data/movies_metadata.csv", stringsAsFactors = FALSE)
```


# Introduction 
Our synergy in our introductory group discussions brought us to a shared
interest in movies and their back-end processes and facts. Thus, we decided
to explore datasets regarding Movies. Jody enjoys comedies. Lynette and
Jeffrey revel in action movies, especially MCU's Avengers. All in the while,
Zhi appreciates romance. There is more than beneath the eye of paying for a
movie stub at the theater as there are many components before and after movie
releases. Some pre-release factors consisting of budgeting, timeline, and
production planning enhance the quality and enjoyability of the movie. While,
a few post-factors incorporate ratings, price, marketing, and theater
distribution network - all of which aim to drive long-term profitability and
to attract a global audience. We are motivated to analyze movie trends,
statistics, and logistics such as calculating maximum and minimum revenues,
obtaining names of most and least profitable movies or genres, computing the
number of tickets sold per movie, and grouping movies based on
ranges of budgets.

# Summary Paragraph (Jody)

# Summary Table 

# Chart 1 (Zhi)
"Insert Chart Intro"
```{r, echo = FALSE, warning = FALSE}
top_ten_chart <- top_10(meta_movie)
ggplotly(top_ten_chart)
```

- One observation about Zhi Chart
- Second observation about Zhi Chart


# Chart 2: Highest Budget on Movie Production Per Year

This chart intends to show the relationship between the maximum budget amounts for movie production from each year. Budget amounts have increased over time as a result of many factors, one being currency inflation and technology equipments and enhancements like CGI used in films.

```{r, echo = FALSE, warning = FALSE}
budget_chart <- budget_by_year(meta_movie)

##Plot Interactive Bar Chart
ggplotly(budget_chart, tooltip = c("year", "max_budget"))
```

- The largest budget spend has been in the year of 2011 with a budget amount of 380 million dollars!
- An upward exponential growth of budgeting is seen to accelerate beginning around the 1970s to 1980s.

# Chart 3 (lynette)

