---
title: "AD Project Movies: Midpoint Deliverable"
author: "Jeffrey Zhao, Jody Wong, Lynette Li, Zhi Ye"
date: "5/22/2019"
output: html_document
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load results from the analysis
# errors and messages will not be printed given the `include = FALSE` option
source("scripts/chart_one.R")
source("scripts/chart_two.R")
source("scripts/chart_three.R")
source("scripts/chart_four.R")
source("scripts/summary_info.R")
source("scripts/summary_table.R")

# Load additional libraries that may be needed for output
library("stringr")
library("plotly")
library("knitr")
library("dplyr")
library("kableExtra")
```

```{r, include = FALSE, echo = FALSE}
meta_movie <- read.csv("data/movies_metadata.csv", stringsAsFactors = FALSE)
movies <- read.csv("data/movies.csv", stringsAsFactors = FALSE)
```


# Introduction 
Our synergy in our introductory group discussions brought us to a shared
interest in movies and their back-end processes and facts. Thus, we decided
to explore datasets regarding Movies. Jody enjoys comedies. Lynette and
Jeffrey revel in action movies, especially MCU's Avengers. All in the while,
Zhi appreciates romance. There is more than beneath the eye of paying for a
movie stub at the theater as there are many components before and after movie
releases. Some pre-release factors consisting of budgeting, timeline, and
production planning enhance the quality and enjoyability of the movie. While,
a few post-factors incorporate ratings, price, marketing, and theater
distribution network - all of which aim to drive long-term profitability and
to attract a global audience. We are motivated to analyze movie trends,
statistics, and logistics such as calculating maximum and minimum revenues,
obtaining names of most and least profitable movies or genres, computing the
number of tickets sold per movie, and grouping movies based on
ranges of budgets. The source of the dataset for our project can be found
[here](https://www.kaggle.com/rounakbanik/the-movies-dataset/version/7).

# Summary Paragraph
Within the movies_metadata file, there were significant information
that were interesting. The longest runtime of a movie was
**`r get_summary_info(meta_movie)[1]`** minutes. That movie was
_`r get_summary_info(meta_movie)[2]`_. The movie
_`r get_summary_info(meta_movie)[3]`_, is significant because it has the
highest vote count compared to any other movie. The tagline of
_`r get_summary_info(meta_movie)[3]`_ is
"`r get_summary_info(meta_movie)[4]`" Also, the movie with the highest
revenue is _`r get_summary_info(meta_movie)[5]`_.

# Summary Table of Top 25 Grossing Movies
```{r, echo = FALSE, warning = FALSE}
aggregate_table <- get_summary_of_top_25(meta_movie)
kable(aggregate_table, col.names = c("Title", "Revenue", "Budget",
                                     "Avg Vote Out of 10")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed",
                                      "responsive"), full_width = FALSE)
```
This table exhibits the top 25 movies based on revenues, depicting the
maximum money a movie is able to generate. In addition, budget and votes
are displayed in order to supplement, in general, the movies' success.
Consistently, the top 25 movies demonstrate high revenues, with typically
a more costly budget and higher ratings!

- The highest budget movie is Avatar, with a budget of 237000000.

- The top 5 movies in terms of revenue are Avatar,
Star Wars: The Force Awakens, Titanic, The Avengers, and Jurassic World.

- At the bottom of the top 25 grossing movies is Alice in Wonderland with
a revenue of 1025491110, a budget of 200000000, and an avg. vote of 6.4.

# Chart 1: Top 10 Most Voted Movies

The purpose of this lollipop chart is to display the top 10 most voted movies.
Each movie is ordered from least to most (left to right). The thin line and 
circle top provides more emphasis on the values of each movie, while giving
it a nice and modern look. 

```{r, echo = FALSE, warning = FALSE}
top_ten_chart <- top_10(meta_movie)
ggplotly(top_ten_chart)
```

- The number one most voted movie is Inception with 14,075 votes.
- The tenth most voted movie from this chart is The Hunger Games, which
has 9,634 votes. 

# Chart 2: Highest Budget on Movie Production Per Year

This chart intends to show the relationship between the maximum budget
amounts for movie production from each year. Budget amounts have increased
over time as a result of many factors, one being currency inflation and
technology equipments and enhancements like CGI used in films.

```{r, echo = FALSE, warning = FALSE}
budget_chart <- budget_by_year(meta_movie)

## Plot Interactive Bar Chart
ggplotly(budget_chart, tooltip = c("year", "max_budget"))
```

- The largest budget spend has been in the year of 2011 with a budget
amount of $380 million!
- An upward exponential growth of budgeting is seen to accelerate
beginning around the 1970s.

# Chart 3: Most Popular Genres

This chart has shown the top 10 most common single and mixed genre for
all kinds of movies that have been released before. The chart is to reflect
the variance of different types genres with the change of number of movies.
I made it into an order start from the least common genres to the most common
genres in the top 10 popular genres because I want readers to quickly see the
order of the most popular 10 types of genres in an order.

```{r, echo = FALSE, warning = FALSE}
genre_popular_chart <- popular_genre(movies)

## Plot Interactive Bar Chart
ggplotly(genre_popular_chart)
```

- What's obvious at a glance is that Drama is the most common genre type.
Comedy is the second popular genre type and Documentary is the third common
genre type in all movies.

- There is an obvious gap between the top three popular genre type compared
to the rest seven types. The rest seven types lie between 1000 to 2000.
However, the top three lie above 4000.

# Chart 4: Correlation between Movie Run Time and Earned Revenue
This chart aims to answer the question whether run time of movies has
correlations with the amount of revenues gained upon release of
the movies. *Question at Hand:* Is there a correlation between
run time and revenue?
```{r, echo = FALSE, warning = FALSE}
scatter_run_rev <- correlation(meta_movie)

## Plot Interactive Bar Chart
ggplotly(scatter_run_rev)
```

- There is low to medium correlation between run time and revenue.

- Vast majority movies are not that profitable regardless of run time
without taking into account currency inflation and time period. Some movies
are seen to be following the correlation in terms of longer movies being
more profitable in revenues and medium length movies generating fair
amounts of revenue.
